\normalfont\spacedallcaps{Language reclamation: Literature review}

### 2023-06-19 assignment-4/article.tex
Remove comments
Solve 18.2

%% \subsubsection*{Explicit GAN loss}

%% From \citet{prince2023understanding} the GAN loss function is as follows:

%% %% This is the characterisation of the saddle points
%% \begin{equation*}
%% \hat{\theta} = \textrm{argmax}_\theta \left[ \min_\phi \left[ \sum_j - \log(1 - D(G(z_j, \theta), \phi))) - \sum_i \log(D(x_i, \phi))) \right] \right]
%% \end{equation*}

%% where $\theta$ represents the weights of the generator function $G$, and $\phi$ is the weights of the discriminator $D$, and $\sigma$ is the sigmoid logistic function.

@@

>>>>

@@

\subsubsection*{Problem 18.2 solution}

$\mathbb{E}[z] = 0$ holds by linearity of expectation since $\mathbb{E}[\epsilon_1] = \mathbb{E}[\epsilon_2] = 0$.

We calculate $Var[z]$ by hand, using the facts that $\epsilon_1$ and $\epsilon_2$ are independent, so $Cov[\epsilon_1, \epsilon_2] = 0$, and $Var[\epsilon_1] = Var[\epsilon_2] = 1$.

\begin{align*}
  Var[z] &= Var[a \epsilon_1 + b \epsilon_2] \\
  &= a^2 Var[\epsilon_1] + b^2 Var[\epsilon_2] + 2ab Cov[\epsilon_1, \epsilon_2] \\
  &= a^2 Var[\epsilon_1] + b^2 Var[\epsilon_2] \\
  &= a^2 + b^2
\end{align*}
